Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-22 Papers/ms.tex
Dye et al

\section{The Cosmic Horseshoe}
As a further demonstration the method, we apply it to the X-band data
from the Isaac Newton Telescope (INT). This image of the Cosmic Horseshoe
\citep{}, which is shown in Figure~\ref{fig:horseshoe_image}. For this system,
more data is available (Y and Z band data, as well as more recent
Hubble Space Telescope (HST) imaging). Unfortunately our current implementation
doesn't allow for multi-band data (unlike \citet{2011MNRAS.412.2521B}), and
is quite slow when running on the larger HST image. Therefore this section
should be considered a further demonstration of the technique, and not a
thorough study of this system.

@@

%The field of view of the image is $15.3180" \times 15.3180"$, and the size is $46 \times 46$ pixels, therefore one pixel is equivalent to $0.33"$. \\
%The method discussed  in the previous section is applied to two models, the first model consist of a flexible source and a Singular Isothermal Elliptical(SIE) model for the lens. This model is has been used often  \cite{Dye2008}, \cite{schneider_falcoa_Ehlers_1994},      . 
%The second model has in addition to the flexible source and SIE, also possible satellites. \\
%The amount of added satellites is automatically determined by the program. If models the addition of an satellite galaxies gives a higher probability it will be preferred over then model without satellite galaxies.  \\
%In both models the SIE is specified by the usual parameters: the location of the SIE ($x_c$,$y_c$), b, axis ratio $f$\footnote{in the code denoted with $q$},  the core radius$\zeta$, $\theta$, shear $\gamma$, and $\theta_{\gamma}$ \cite{kormann_schneider_1994}.\\

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{horseshoe_image.pdf}
\caption{\label{fig:horseshoe_image}}
\end{center}
\end{figure}

@@

>>>>

\section{The Cosmic Horseshoe}
As a further demonstration the method, we apply it to the X-band data
of the Cosmic Horseshoe \citep{2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:horseshoe_image}.
For this system,
more data is available (Y and Z band data, as well as more recent
Hubble Space Telescope (HST) imaging). Unfortunately our current implementation
doesn't allow for multi-band data (unlike \citet{2011MNRAS.412.2521B}), and
is quite slow when running on the larger HST image. Therefore this section
should be considered a further demonstration of the technique, and not a
thorough study of this system.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{horseshoe_image.pdf}
\caption{The X-band INT image of the Cosmic Horseshoe.
\label{fig:horseshoe_image}}
\end{center}
\end{figure}

@@

@@

\bibitem[\protect\citeauthoryear{Dye et al.}{2008}]{2008MNRAS.388..384D} 
Dye S., Evans N.~W., Belokurov V., Warren S.~J., Hewett P., 2008, MNRAS, 
388, 384
